Detection of slow slip events using wavelet analysis of GNSS recordings

### 2021-12-01 paper/paper_bssa.tex
Make figures for movie

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{authblk}
\usepackage{color}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{natbib}
\usepackage{url}

@@

\title{Detection of slow slip events using wavelet analysis of GNSS recordings}
\author[1]{Ariane Ducellier}
\author[1]{Kenneth C. Creager}
\author[1]{David A. Schmidt}
\affil[1]{University of Washington, Department of Earth and Space Sciences, Box 351310, 4000 15th Avenue NE Seattle, WA 98195-1310}
\date{}

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{authblk}
\usepackage{color}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{url}

@@

\title{Detection of slow slip events using wavelet analysis of GNSS recordings}
\author[1]{Ariane Ducellier}
\author[2]{Kenneth C. Creager}
\author[2]{David A. Schmidt}
\affil[1]{Corresponding author. University of Washington, Department of Earth and Space Sciences, Box 351310, 4000 15th Avenue NE Seattle, WA 98195-1310}
\affil[2]{University of Washington, Department of Earth and Space Sciences}
\date{}

@@

\doublespacing
